%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,10pt]{article} % 改為10pt
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins (可根據需要進一步微調)
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4pt}

% Sections formatting: 減少一些垂直間距
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-1pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{1pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]} % 調整左邊距
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\huge NIALL ZHANG}} & Email: \href{mailto:niall.zhang.hc@gmail.com}{niall.zhang.hc@gmail.com} \\
  \href{https://www.linkedin.com/in/niall-z/}{http://linkedin.com/in/niall-z} & Mobile: \href{tel:+1(672)515-2141}{+1(672)515-2141} \\
  \href{https://github.com/Niall-Zhang}{https://github.com/Niall-Zhang} & Vancouver, BC\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New York Institute of Technology}{Vancouver, BC}
      {Master of Science in Cybersecurity}{Jan 2023 - Oct 2024}
    \resumeSubheading
      {University of British Columbia}{Vancouver, BC}
      {Bachelor of Science in Physics}{Sep 2018 - May 2022}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Arspace Technology Ltd. (Start-up)}{Vancouver, BC}
      {Software Engineer (Part-Time)}{Jan 2024 - Aug 2024}
      \resumeItemListStart
        \resumeItem{}
          {Built and launched a cross-platform mobile application enabling users to purchase event tickets and match with potential dates, deployed on both the Apple App Store and Google Play.}
        \resumeItem{}
          {Designed and implemented a backend using \textbf{Python} \textbf{Django} featuring authentication, user registration, and an admin dashboard. Integrated RESTful APIs, OAuth, and Stripe to enable rapid development and scalability; designed the relational schema and deployed the \textbf{PostgreSQL} database on \textbf{GCP Compute Engine}.}
        \resumeItem{}
          {Utilized \textbf{Flutter} to develop a mobile frontend with a consistent UI across iOS and Android, delivering an optimal user experience.}
      \resumeItemListEnd

      \resumeSubheading
      {New York Institute of Technology}{Vancouver, BC}
      {Teaching Assistant}{May 2024 - Jul 2024}
      \resumeItemListStart
        \resumeItem{}
          {Assisted a professor in delivering the \textbf{Embedded System Security} course, supporting 28 students in deepening their understanding through both academic theory and industry experience.}
        \resumeItem{}
          {Contributed to designing and grading assignments, conducting lab sessions, and holding office hours and tutorials.}
      \resumeItemListEnd

      \resumeSubheading
      {ezSec Inc.}{Remote, Canada}
      {Cybersecurity Data Analyst Intern}{Feb 2024 - May 2024}
      \resumeItemListStart
        \resumeItem{}
         {Developed a machine learning-based cybersecurity analysis framework to automatically detect threats using MITRE ATT\&CK techniques and open-source data.}
        \resumeItem{}
         {Implemented \textbf{Python} scripts to scrape, clean, and process cybersecurity alerts in Yara, YAML, and HTML formats from authoritative public sources, transforming data into CSV files for analysis.}
        \resumeItem{}
         {Designed regex rules for alerts and mapped them to MITRE ATT\&CK techniques, expanding the lookup table by 300\%.}
        \resumeItem{}
         {Enhanced an NLP model by integrating Attack Patterns from STIX, boosting accuracy from 40\% to 62\%.}
      \resumeItemListEnd

      \resumeSubheading
      {iFlytek Corp.}{Hefei, China}
      {Software Engineer Intern}{Apr 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItem{}
          {Contributed to a smart city traffic police project in \textbf{Java} for detecting if cars yielded to pedestrians.}
        \resumeItem{}
          {Collaborated with a UI designer to implement \textbf{Vue.js} modules based on Figma designs, enhancing feature reusability and modularity.}
        \resumeItem{}
          {Developed an API using \textbf{Java Spring Boot} and an \textbf{OpenCV} model to analyze live camera feeds, improving detection accuracy by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Project}
  \resumeSubHeadingListStart
    \resumeSubItem{Time Management Web App}{: Developed a time management web application using a full JavaScript stack with React for the front end and Node.js with Express for the RESTful API. Followed SDLC and Agile methodologies, implemented comprehensive QA testing (including API/integration tests through Postman), and managed version control with Git.}

  \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS------------
\section{Technical Skills}
\small
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
  \item \textbf{Languages}: Python, Java, JavaScript
  \item \textbf{Front End}: Vue.js, React, Flutter, HTML5, CSS3
  \item \textbf{Back End}: Node.js, Spring Boot, Django
  \item \textbf{Cloud}: GCP (IAM, Cloud Storage, Compute Engine, APIs \& services)
  \item \textbf{Database}: SQL Server, MongoDB, SSIS, SSMS, SQL Report Builder
\end{itemize}

\end{document}
